\section{Scenarios}

\subsection{Scenario - Stefan}
Stefan is in a café right now.
Today he travels alone and without his usual friends.
He wants to beautify his profile on UK4You with newly learned skills so that potential employers are aware of him and his skills.
Stefan pulls out his phone and starts editing his profile page.
He has recently learned the Python programming language and feels comfortable with it.
For this reason, he enters Python as a skill under the Skills category.
However, he thinks that it might also make sense to register his participation in the university's coding club there.
So he enters this as well.
Suddenly Stefan receives a notification.
He is curious and clicks the notification.
Max1337 wrote a comment to Stefan under his skill Python: "As if you know Python what nonsense".
The automatic filter system has put the comment on-hold, which is why it is not yet visible to everyone.
Stefan thinks that this comment shouldn't visible and simply removes it.
After he removed the comment he opens the job page of the UK4You platform and looks at the different employers.
Several suggestions are already made there based on Stefan's skills.
However, he has the option to change this filter and adjust his own filter options.
With one click he sends several applications to different companies.
After doing that, he packs his cell phone back to enjoy his coffee.

\subsection{Scenario - Maria}
Maria is currently going through her daily social media routine.
She has decided to check the most important information once a day.
She just finished checking out the posts on Mastodon, a decentralized alternative to Twitter.
Maria would now like to scroll through UK4You to see the current academic work at her university.
On the timeline, she sees all the posts from all the academics she follows.
She follows current research so closely because she is interested in participating.
Fortunately, she sees a post where a professor calls for participation in a research project.
She wants to find out more and clicks on the professor's profile.
She sees that the professor has many publications and that they also represent topics in her field of interest.
For this reason, Maria decides to contact the professor.
With the help of a button, she can express her interest in the research work.
