\section{Value Sensitive Design}\label{sec:vsd}
VSD is a design that takes human values into account\cite{friedman-vsd}.
There are many values that are important for the creation of the UK4You platform.
As already mentioned in the introduction in \autoref{sec:introduction}, the main focus of the platform is to be as productive and inclusive as possible.
But there are also many other values like privacy, productivity, trust, ownership, freedom from bias, usability, accessibility and informed consent.
In order to guarantee the values, an understanding must first be created of how these values are defined.
This is done using the privacy value as an example.\\

% Reason how might the value of privacy be defined?
Let's first take a look at a well-known dictionary: The Oxford English Dictionary.
There are two different definitions from the Oxford English Dictionary\cite{oxford-dictionary}.
The first one defines privacy as the state of being alone and not watched or disturbed by other people.
The second one defines it as the state of being free from the attention of the public.
Let's also look at the etymology, i.e. the word origin, of the word privacy.\\

According to Etymonline, an online etymology dictionary, the word privacy comes from the word private\cite{etymonline}.
It was used around the year 1600 and is the noun of the word private.
Private originally comes from the Latin word privatus, which means "personal or belonging to oneself". % Cite?
This is in contrast to the word public.
The origin comes from a time when things were either owned by the state or by an individual.
For this reason, privatus can also mean "not belonging to the state" and publicus, the Latin translation of public, "belonging to the state". \\ % cite?

The exact historical origins are difficult to define.
It is clear that figures such as Aristotle have already philosophized on this subject\cite{stanford-philosophy}.
He thought about a public sphere, where political activity takes place and a private sphere that is more focused on family and domestic life.
The word "Privatsphäre" (literally privatsphere), which comes from the German and is the translation of privacy, is probably a reference to this idea.
Another definition of the word privacy comes from Old French in the late 14th century and means secret or solitude.\\

The various definitions and ideas were then first described as a human right in 1891\cite{history-of-privacy}.
There, the American lawyers Samuel Warren and Louis Brandeis defined privacy as "the right to be let alone".
In 1967, professor of public law and government Alan Furman Westin published a book called Privacy and freedom\cite{privacy-and-freedom}.
He describes privacy as the claim to determine the extent to which information is shared with others.
To date, however, it is difficult to grasp all the different meanings and interpretations of privacy.
Privacy can therefore be understood as a complicated construct made up of different definitions and contexts in which they take place.\\

% Is it in conflict with any other values on your list? 
If certain processes or data are not transparent, then this can be due to the affiliation of privacy.
For example, a company does not want to publish certain data sets or processes because others could generate revenue from them.
However, the lack of transparency prevents the building of trust and a subsequent informed consent.
Usability can also be restricted if, for example, a person is not interested in passing on location data.
As a result, further functionalities could be lost and the user experience could deteriorate.

% Can you propose technological solutions that safeguard the value of privacy and make the users aware of privacy as a value? 
There are various ways to ensure privacy.
As mentioned earlier, it is important that users own their data and have the right to access and delete it.
Data should also be encrypted in the database so that hackers cannot access clear text data directly in the event of a breakthrough.
Pseudonyms could also be used to make users anonymous.
However, the following section explains why this is not done.\\

% Speculate: should this value be challenged? If so, why and how?
Privacy as a value should be challenged as it is a human right.
There should be the right to switch data back to private.
There are numerous examples that illustrate this.
Taking and posting an unauthorized photo should be reversible.
Likewise, personal data should not be passed on or sold to third parties.
This can have serious consequences in the case of stalking or spamming.
It should always be up to everyone how much they share and publish on the Internet.

\subsection{Pseudonyms}
This section explains why pseudonyms are not a good idea at Uk4You.
But why not? Pseudonyms have many positive aspects.
They ensure that users can post content anonymously.
Any person could redefine themselves and get a free pass to belong to a privileged group.
Gender, age, social, cultural or economic class could all be redefined.
This could also ensure that people are freed from social prejudices.
The well-known saying \glqq On the Internet, nobody knows you're a dog\grqq{} exaggerates this opportunity of assigning any possible identity\cite{steiner-internet-dog}.
The problem with this type of pseudonymization is that hiding social prejudices doesn't solve them.
Rather, the opposite could be true, being amplified when everyone joins the privileged group on the internet through false identities.\\

Another positive aspect is that there is less of a hurdle to post otherwise critical content.
The advantage is that people could dare more without it being their fault.
But this is exactly where the problem lies.
People would have a lower hurdle to insult or spread fake information.
After all, there is no traceable consequence in real life.\\

The best way to demonstrate this is with a short scenario.
This scenario is about Max, a student who got his grade back in Computing and Society 2 and is extremely dissatisfied.
Using a pseudonym and a completely new account, he logs into Uk4You.
Because of his emotional state, he writes a message full of insults to the supervisor of Computing and Society 2.
How unfair everything is, how badly the course is structured, etc.
Due to the high number of participants, it is not easy for the supervisor to trace who this person might be.\\

Presumably the course instructor handles this situation professionally and asks more questions in order to be able to understand the situation.
However, not everyone can handle this so easily.
Especially interactions between two emotionally charged students can be very critical.
From this scenario and the previous arguments it can be concluded that pseudonyms, but also throwaway accounts, are not a good solution for UK4You.
However, it could be considered in the future to activate special anonymous forums or post content in order to deliberately lower this hurdle.
